\documentclass[a4paper]{article}
%\usepackage{amsfonts}
%\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage[utf8]{inputenc}
%\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
%\usepackage{subfig}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{siunitx}
%\sisetup{retain-zero-exponent=true}%
\newminted{py}{%
%		linenos,
		fontsize=\small,
		tabsize=2,
		mathescape,
}
\newminted{text}{%
%		linenos,
		fontsize=\small,
		tabsize=2,
		mathescape,
}

\title{Lab 3: Significance of network metrics}
\author{Rodrigo Arias Mallo}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}
\subsection{The metric}

For selecting the metric, I set the seed to the last 5 digits of my DNI, as 
recently seen in some hash generation\footnote{	
\url{http://klondike.es/klog/2017/09/25/descifrando-las-bases-de-datos-del-referendum-catalan/}}, 
and ran the following command in python:
%
\begin{pycode}
from random import *

seed(64718)
metrics = ["clustering coefficient", "closeness centrality"]
r = randint(0, 1)

print(metrics[r])
\end{pycode}
%
Which produced the following output
%
\begin{textcode}
% python metric.py
clustering coefficient
\end{textcode}
%
So I decided to use clustering coefficient $C_{WS}$ as the metric $x$.


\subsection{Cleaning the data}

The datasets have been uncompressed in \texttt{data/}, and then processed by the 
script \texttt{prepare-data.sh}, which removes the header with the number of 
nodes and edges, and outputs the remaining edge list in the same file with a new 
extension \texttt{.edges}. The properties of the graphs can be seen at the 
table~\ref{tab:prop}.

\begin{table}[h]
	\centering
	\input{table1.tex}
	\caption{Properties of the graphs after preproccesing.}
	\label{tab:prop}
\end{table}

\section{Experiments}

Based on some properties of a graph $G$, we want to create a sequence of random 
graphs $\langle G \rangle$ by using two different methods, and then test if they 
maintain a set of measures that we found on $G$.

The first model, the Erdös--Rényi graph takes as input the number of vertex 
$|V|$ and edges $|E|$ of $G$, and builds a new random graph with the same number 
of vertex and edges. The clustering coefficient is then computed for each graph 
in the sequence $\langle G_{ER} \rangle$ as $\langle x_{ER} \rangle$.
The switching model also produces a sequence of graphs $\langle G_S \rangle$ and 
the measurements $\langle x_S \rangle$.

\subsection{Erdös--Rényi model}

The ER model is implemented in \texttt{python} using the \texttt{networkx} 
package.  The \texttt{gnm\_random\_graph} creates a ER graph with parameters 
$|V|$ and $|E|$. An average of $T = 25$ graphs is performed. The measure is 
taken by calling \texttt{average\_clustering}.
%
\begin{table}[h]
	\centering
	\input{table2.tex}
	\caption{The measures of ER model.}
	\label{tab:er}
\end{table}

We see that none of the generated graphs contain a value greater than the 
original one. We can conclude that, even the ER model keeps the number of nodes 
and edges, the clustering coefficient is smaller.

\subsection{Switching model}

This model is implemented in the R package BiRewire\cite{birewire} written by A.  
Gobbi, a fast implementation of the switching model \cite{gobbi14} 
\cite{gobbi17} with especial design for large graphs. The algorithm switches two 
edges while the degree distribution is kept. Given two edges $(u,v),(s,t)$, with 
all different vertex, the switches $(u,t), (s,v)$ and $(u,s), (v,t)$ are 
randomly performed, when no loops or multi-edges are introduced. A total of $T = 
25$ graphs are generated, starting with the graph for each language, and with a 
number of steps equal to $Q = |E|\log|E|$.  The clustering coefficient is 
computed by the function \texttt{transitivity(g, type='localaverage', 
isolates='zero')} and tabulated for each language in table~\ref{tab:switch}.
%
\begin{table}[h]
	\centering
	\input{table3.tex}
	\caption{The measures of the switching model.}
	\label{tab:switch}
\end{table}
%
\section{Results}

In the ER model, the clustering coefficient is always smaller compared to the 
original graph. However, using the switching model the measures are similar, but 
sometimes still small.

\section{Discussion}

I don't know what is the effect of the model in the clustering coefficient, nor 
by what means can I learn that relation. Neither I understand the utility of 
especulating about such relation, at least without the ability of designing a 
posterior test of my hypothesis.

\section{Methods}

To avoid the low speed of the computation, I tested with some libraries that 
implement a efficient representation of the graph, and I found the BiRewire to 
be acceptable and simple. Also the \texttt{networkx} package has a very good 
documentation, and implements a lot of random generators, including the ER 
model.

I decided not to optimize anything without a good reason to do it\footnote{``The 
real problem is that programmers have spent far too much time worrying about 
efficiency in the wrong places and at the wrong times; premature optimization is 
the root of all evil (or at least most of it) in programming''-- Donald Knuth}; 
i.e.  after a thorough analysis. As the computation time was not too large, I 
avoided the selection of some advanced data structure to perform the 
computations.

\bibliographystyle{unsrt}
\bibliography{biblio}

\end{document}
